Exploiting First-Class Arrays in Fortran for Accelerator Programming

### 2010-12-03 opencl/papers/foropencl.tex
updates for conference format
more

\documentclass{article}

\title{ForOpenCL: Examing Fortran as a base language for accelerated platforms:
I forgot what we decided upon}
\author{Awesome Fortran Programmers}

@@

Similar to ZPL.

>>>>

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\usepackage{cite}
\usepackage{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{array}
\usepackage{url}

\title{Exploiting First-Class Arrays in Fortran for Accelerator Programming}
\author{Awesome Fortran Programmers}

@@

Fortran 90 introduced a rich array syntax that allows programmers to
write code that is in terms of whole arrays or subarrays, with data
parallel operators to compute on the arrays.  This has the benefit of
avoiding explicit looping in the code and maintaining a high-level
style that is closer to the original mathematical specification of the
problem being solved.  More importantly from a compilation
perspective, this defers decisions about how to implement these
whole-array operations to a compilation tool.  When faced with a novel
architecture such as modern GPUs that are ideally suited to data parallel
programming models, the fit between Fortran arrays and these systems is
quite clean.

This paper uses four simple features of Fortran that form a language subset
that does not require any language extensions and can be easily transformed
to a lower level implementation in either CUDA or OpenCL.

\begin{enumerate}
\item Elemental functions
\item Pure procedures
\item Shift operators
\item Array notation
\end{enumerate}

\subsection{Relationship to other languages}

Similar to ZPL, CM5 stencil compilers, CMFortran stuff.
